Reflections from reproductions

### 2024-11-04 pages/reflections.qmd
docs(reflections): update reflections for each item, now that have add hernandez wood and johnson

<!--TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 reflections once have finished reproduction -->

<!--TODO: Check all the notes on Johnson's reflections page are captured below, and that there weren't any new categories to add-->

@@

@@

This summary excludes:

* "Quicker models are easier to work with"
* "For computationally expensive models, state memory usage and provide alternatives for lower spec machines"
* "Avoid large file sizes if possible"
* "Do not output excessive numbers of files"
* "Other"

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files).
* Ideally mention this in repository, not just the paper.
* If there are local dependencies (e.g. other GitHub repositories), make sure to (a) mention and link to these repositories, so it is clear they are also required, and (b) include licence/s in those repositories also, so they can be used.
* This was a common issue.

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

@@

@johnson_cost_2021: <!--TODO-->

@@

<!--TODO: Consider overlap between some of these and how clear it is. I seperated to seperate out the script structure v.s. hard coding v.s. providing parameters and scenarios later. Consider whether evaluation for Shoaib below feels correct or not. -->

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* Design model so that you can re-run it with different parameters without needing to make changes to the model code itself.
    * This allows you to run multiple versions of the model with the same script.
    * It also reduces the likelihood of missing errors (e.g. if miss changing an input parameter somewhere, or input the wrong parameters and don't realise).
* This was an uncommon issue.

@@

@hernandez_optimal_2015: Partially met. Did not hard code, runs, population, generations, and percent pre-screened. However, did hard code other parameters like bi-objective v.s tri-objective model and bounding. Also, it was pretty tricky to change percent pre-screened, as it assumed you provided a `.txt` file for each %.

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* It can be quite difficult to change parameters that are hard coded into the model. Ideally, all the parameters that a user might want to change should be easily changeable and not hard coded.
* This is a somewhat common issue.
* There is overlap between this and whether the code for scenarios is provided (as typically, the code for scenario is conditionally changing parameter values, although this can be facilitated by not hard coding the parameters, so you call need to change the values from "outside" the model code, rather than making changes to the model functions themselves). Hence, have included as two seperate reflections.
* Important to note that we evaluate this in the context of reproduction - and have not checked for hard-coded parameters outside the specified scenario analyses, but that someone may wish to alter if reusing the model for a different analysis/context/purpose.

@@

<!--TODO: Consider whether this is something to keep? Did any have an issue with relative file paths? Or was it more that I saw an issue with relative file paths that were tricky to change? Have mentioned this is a bit under "Saves output to a file". Although maybe it doesn't have to be an issue to mention it - can just be a positive, that noticed all used?-->

@@

**Reflections:** <!--TODO: Update reflections (when add Shoaib, Huang, Lim, Kim and Wood) and then (since have added Johnson, Hernandez and Wood) -->

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) --> Large amounts of code duplication are non-ideal as they can:

* Make code less readable
* Make it trickier to change universal parameters
* Increase the likelihood of introducing mistakes

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* With increasing code complexity, the inclusion of sufficient comments becomes increasingly important, as it can otherwise be quite time consuming to figure out how to fix and change sections of code
* Define abbreviations used within the code
* Good to have consistent comments and docstrings throughout (i.e. on all scripts, on not just some of them)

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* Reduce model run time if possible as it makes it easier to work with, and facilitates doing full re-runs of all scenarios (which can be important with code changes, etc).
    * Relatedly, it is good practice to re-run all scripts before finishing up, as then you can spot any errors like the one mentioned for @kim_modelling_2021
* Common issue (to varying degrees - i.e. taking 20 minutes, up to taking several hours).

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* Some models are so computationally expensive that it may be simply impossible to run it a feasible length of time without a high powered machine.
* If a model is computationally expensive, it would be good to provide suggested alternatives that allow it to be run on lower spec machines
* Not a common problem - only relevant to computationally expensive models

@@

@johnson_cost_2021: Fully met. Could determine appropriate parameters for sensitivity analysis from description in article.

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* Don't provide alternative results for the same metrics
* Make it clear what each colum/category in the results table means, if it might not be immediately clear.

@@

**Reflections:** <!--TODO: Update reflections once add Johnson -->

* For most studies, this was not relevant, with outputs relatively small
* I only really found this to be an issue when files exceeded GitHub threshold. [GitHub](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-large-files-on-github) give warning over 50 MB, blocks files over 100 MB, requiring you to use GitHub LFS. Recommends repositories ideally <1 GB and for sure < 5GB. [GitHub LFS](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-storage-and-bandwidth-usage) has limits on storage and bandwith use (1GB of each).
* **Reducing file size isn't the only solution**. In cases where you have large files, a good option can be storing it elsewhere and then pulling from there into your workflow - for example, storing in **zenodo** and fetching using [pooch](https://github.com/fatiando/pooch).

@@

@@

I have not evaluated like as a criteria, as a large number of files is not inherently a bad thing, and might be difficult to avoid.

@@

**Reflections:** <!--TODO: Update reflections once add Johnson -->

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* Depending on your model and the outputs/type of output you are looking at, the lack of seeds can have varying impacts on the appearance of your results, and can make the subjective judgement of whether results are consistent harder (if discrepancies could be attributed to not having consistent seeds or not).
* It can be really quite simple to include seeds.

@@

<!--TODO: Lim 2020... I think from memory that this output tables  similar to the paper, but I then changed them as that format was difficult to compare/work with -->

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* It can take a bit of time to do this processing, so very handy for it to be provided.
* Common issue.

@@

@huang_optimizing_2019: Not met. Had to write code from scratch. For one of the figures, it would have been handy if informed that plot was produced by a simmer function (as didn’t initially realise this). It also took a bit of time for me to work out how to transform the figure axes as this was not mentioned in the paper (and no code was provided for these). It was also unclear and a bit tricky to work out how to standardise the density in the figures (since it is only described in the text and no formula/calculations are provided there or in the code). <!-- TODO: Consider whether this should be split into another box (i.e. about providing the processing?) -->

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* It can take a bit of time to do this processing, particularly if the figure involves any transformations (and less so if the figure is simple), so very handy for it to be provided.
* Common issue.

@@

* Provide code to calculate in-text results
* Common issue

@@

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

* Even if as simple as running a script, include instructions on how to do so
* Common issue

@@

<!--TODO: Reflect whether any of these should be boxes above-->

@@

<!--TODO: update or remove this summary-->

* Include grid lines
* Include data dictionaries
* If feasible, maintain code to avoid dependency on unsupported old versions of packages and languages
* Ideally, include copies of your results, so can (a) compare against, (b) use to run analysis on, and (c) use in troubleshooting

>>>>

@@

<!-- TODO: From Tom - So much great work and interesting findings. We need to move towards some headlines and take aways for the community. Mayybe there are some high level groupings of your findings? e.g.

* Study reporting
* Model structuring and functionality
* Analysis pipeline

Or perhaps:

* Evidence supporting the use of reporting guidelines
    * as in - reporting guidelines state this should info be included and you found it v.difficult or impossible to reproduce without it.?
-->

@@

This is a summary of all the items that were evaluated (with ✅🟡❌) below.

@@

* The `import` statements can be sufficient in indicating all the packages required but this is not always the case if there are "hidden"/unmentioned dependencies that don't get imported
* There are various options for listing the packages (e.g. comprehensive import statements, installation lines in the script, environment files, package DESCRIPTION file).
* Ideally mention this in repository, not just the paper.
* If there are local dependencies (e.g. other GitHub repositories), make sure to (a) mention and link to these repositories, so it is clear they are also required, and (b) include licence/s in those repositories also, so they can be used.
* This was a common issue.

@@

@@

@johnson_cost_2021: Fully met. Model provided as a package (which is an R interface for the C++ model).

@@

@@

* Design model so that you can re-run it with different parameters without needing to make changes to the model code itself.
    * This allows you to run multiple versions of the model with the same script.
    * It also reduces the likelihood of missing errors (e.g. if miss changing an input parameter somewhere, or input the wrong parameters and don't realise).
* This was an uncommon issue.
* Note, this just refers to the basic set-up, with items below like hard coding parameters also being very important in this context.

@@

@hernandez_optimal_2015: Partially met. Did not hard code runs, population, generations, and percent pre-screened. However, did hard code other parameters like bi-objective v.s tri-objective model and bounding. Also, it was pretty tricky to change percent pre-screened, as it assumed you provided a `.txt` file for each %.

@@

* It can be quite difficult to change parameters that are hard coded into the model. Ideally, all the parameters that a user might want to change should be easily changeable and not hard coded.
* This is a relatively common issue.
* There is overlap between this and whether the code for scenarios is provided (as typically, the code for scenario is conditionally changing parameter values, although this can be facilitated by not hard coding the parameters, so you call need to change the values from "outside" the model code, rather than making changes to the model functions themselves). Hence, have included as two seperate reflections.
* Important to note that we evaluate this in the context of reproduction - and have not checked for hard-coded parameters outside the specified scenario analyses, but that someone may wish to alter if reusing the model for a different analysis/context/purpose.

@@

@@

* This was not an issue for any studies - but included to note this was a "facilitator", as would have needed to amend if they weren't.

@@

**Reflections:** Large amounts of code duplication are non-ideal as they can:

* Make code less readable
* Make it trickier to change universal parameters
* Increase the likelihood of introducing mistakes
* Make it trickier to set up scenarios/sensitivity analyses

@@

* With increasing code complexity, the inclusion of sufficient comments becomes increasingly important, as it can otherwise be quite time consuming to figure out how to fix and change sections of code
* Define abbreviations used within the code
* Good to have consistent comments and docstrings throughout (i.e. on all scripts, on not just some of them)
* Common issue

@@

* Reduce model run time if possible as it makes it easier to work with, and facilitates doing full re-runs of all scenarios (which can be important with code changes, etc).
    * Relatedly, it is good practice to re-run all scripts before finishing up, as then you can spot any errors like the one mentioned for @kim_modelling_2021
* Common issue (to varying degrees - i.e. taking 20 minutes, up to taking several hours or even day/s).

@@

* Some models are so computationally expensive that it may be simply impossible to run it a feasible length of time without a high powered machine.
* Handy to mention memory requirements so someone with lower spec machine can ensure they would be able to run it.
* If a model is computationally expensive, it would be good to provide suggested alternatives that allow it to be run on lower spec machines
* Not a common problem - only relevant to computationally expensive models

@@

@johnson_cost_2021: Fully met. Could determine appropriate parameters for sensitivity analysis from figures in article.

@@

* Don't provide alternative results for the same metrics
* Make it clear what each colum/category in the results table means, if it might not be immediately clear.
* Make differences between seperate results tables clear.

@@

* For most studies, this was not relevant, with outputs relatively small.
* I only really found this to be an issue when files exceeded GitHub threshold. [GitHub](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-large-files-on-github) give warning over 50 MB, blocks files over 100 MB, requiring you to use GitHub LFS. Recommends repositories ideally <1 GB and for sure < 5GB. [GitHub LFS](https://docs.github.com/en/repositories/working-with-files/managing-large-files/about-storage-and-bandwidth-usage) has limits on storage and bandwith use (1GB of each).
* **Reducing file size isn't the only solution**. In cases where you have large files, a good option can be storing it elsewhere and then pulling from there into your workflow - for example, storing in **zenodo** and fetching using [pooch](https://github.com/fatiando/pooch).

@@

<!--TODO: Move this to other, or move things from other up here into their own boxes -->

@@

I have not evaluated this as a criteria, as a large number of files is not inherently a bad thing, and might be difficult to avoid.

@@

@@

* Depending on your model and the outputs/type of output you are looking at, the lack of seeds can have varying impacts on the appearance of your results, and can make the subjective judgement of whether results are consistent harder (if discrepancies could be attributed to not having consistent seeds or not).
* It can be really quite simple to include seeds.
* Over half of the studies did include seed control in their code.

@@

@@

* It can take a bit of time to do this processing, and it can be tricky/confusing to do correctly, so very handy for it to be provided.
* Common issue.

@@

@huang_optimizing_2019: Not met. Had to write code from scratch. For one of the figures, it would have been handy if informed that plot was produced by a simmer function (as didn’t initially realise this). It also took a bit of time for me to work out how to transform the figure axes as this was not mentioned in the paper (and no code was provided for these). It was also unclear and a bit tricky to work out how to standardise the density in the figures (since it is only described in the text and no formula/calculations are provided there or in the code).

@@

* It can take a bit of time to do this processing, particularly if the figure involves any transformations (and less so if the figure is simple), so very handy for it to be provided.
* Also, handy if the full code can be provided for all figures (although partial code is more helpful than none at all).
* Common issue.

@@

* Provide code to calculate in-text results
* Universal issue, for those with in-text results not otherwise captured in tables and figures

@@

* Even if as simple as running a script, include instructions on how to do so
* In simpler projects (e.g. single script), this can be less of a problem.
* Common issue

@@

@@
